The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-16 dit-paper_ieee.tex
added equation numbering

		Mathematically,
		\[
			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
		\]
		where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ which arrival times
		and deadlines are both in the closed interval $[t_1, t_2]$.

		The values of the $n_i$ are given by \cite{baruah1999generalized}
		\[
			n_i(t_1, t_2) =
			\left\llbracket
				\left\lfloor
					\frac{t_2 - O_i - D_i}{T_i}
				\right\rfloor -
				\left\lceil
					\frac{t_1 - O_i}{T_i}
				\right\rceil + 1
			\right\rrbracket_0
		\]
		where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.

@@

		\begin{theorem}
		\[
			\begin{array}{c}
				\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
				\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
			\end{array}
		\]
		\end{theorem}

@@

      The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility. They can all be written in the following way:
      \[
     	\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
      	t_1 \leq t_2
      \]
      Note that for a given $t$, we have that the $n_i(t)$ are
      constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

@@

  The value of the first DIT can be found by solving the following modular equation system:
	\[
		t_d = \min
		\left( t \; s.t. \; \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]:
			\left\{
				\begin{array}{c}
					t > 0 \\
					t \equiv a_i \; (mod \; T_i) \\
				\end{array}
			\right.
		\right)
	\]
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

  For synchronous systems in which the execution times are not known, the first DIT $t_d$
  is our ``best guess'' at an upper limit on the end of the busy period. As it was sufficient
  to check the DBF test in intervals $[0, t]$ before the end of the busy period, it is
  slightly more pessimistic but still correct to use the following condition:
  \[
  		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d
  		\iff \text{The system is feasible}
  \]

@@

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
				T_i] \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \;	T_i)
						\\
					\end{array}
				\right.
			\end{array}
		\]

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]
		which means that there could be systems with no FPDIT.
		We now present an example of such a system.\\

@@

	We observe that when the $CDF$ tends to zero, few systems have a FPDIT.
	This is easily explained by the fact that
	a high CDF means more idle instants for each task, and thus more opportunities
	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
	happen, a higher number of tasks results in a decrease in FPDIT density.

@@

		\[
			\sum_{i=1}^{n} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\]

@@

We now apply Algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
$$
\left\{
  \begin{array}{ccccc}
    & & C_2 & \leqslant & 2 \\
    C_1 & + & C_2 & \leqslant & 7
  \end{array}
\right.
$$
The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.

>>>>

		Mathematically,
		\begin{equation}
			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
		\end{equation}
		where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ which arrival times
		and deadlines are both in the closed interval $[t_1, t_2]$.

		The values of the $n_i$ are given by \cite{baruah1999generalized}
		\begin{equation}
			n_i(t_1, t_2) =
			\left\llbracket
				\left\lfloor
					\frac{t_2 - O_i - D_i}{T_i}
				\right\rfloor -
				\left\lceil
					\frac{t_1 - O_i}{T_i}
				\right\rceil + 1
			\right\rrbracket_0
		\end{equation}
		where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.

@@

		\begin{theorem}
			\begin{equation}
				\begin{array}{c}
					\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
					\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
				\end{array}
			\end{equation}
		\end{theorem}

@@

		The DBF test gives us a list of inequations on the WCET values of the task set
		which together are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for a given $t$, we have that the $n_i(t)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

@@

		The value of the first DIT can be found by solving the following modular
		equation system:

		%TODO : change format so that the equation number is displayed correctly

		\begin{equation}
			t_d = \min
			\left( t \; s.t. \; \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]:
				\left\{
					\begin{array}{c}
						t > 0 \\
						t \equiv a_i \; (mod \; T_i) \\
					\end{array}
				\right.
			\right)
		\end{equation}
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

  For synchronous systems in which the execution times are not known, the first DIT $t_d$
  is our ``best guess'' at an upper limit on the end of the busy period. As it was sufficient
  to check the DBF test in intervals $[0, t]$ before the end of the busy period, it is
  slightly more pessimistic but still correct to use the following condition:
  \begin{equation}
  		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d
  		\iff \text{The system is feasible}
  \end{equation}

@@

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\begin{equation}
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
				T_i] \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \;	T_i)
						\\
					\end{array}
				\right.
			\end{array}
		\end{equation}

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:

		%Review 3 : use ref to justify this formula
		%TODO : change format so that the equation number is displayed correctly

		\begin{equation}
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i,j
		\end{equation}
		which means that there could be systems with no FPDIT.
		We now present an example of such a system.\\

@@

	We observe that when the CDF tends to zero, few systems have a FPDIT.
	This is easily explained by the fact that
	a high CDF means more idle instants for each task, and thus more opportunities
	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
	happen, a higher number of tasks results in a decrease in FPDIT density.

@@

		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}

@@

We now apply Algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
	\begin{equation}
		\left\{
			\begin{array}{ccccc}
				& & C_2 & \leqslant & 2 \\
				C_1 & + & C_2 & \leqslant & 7
			\end{array}
		\right.
	\end{equation}
The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.
